Language-Based Security for Low-Level MPC

### 2024-07-17 ppdp24/bruteforce.tex
checkpoint

In Figure \ref{fig-solve} we define the algorithm
$\solve{\stores}{\be}{\cid}$ which filters a given $\stores$ to obtain
the subset whose elements satisfy $\be$. In this Figure and elsewhere
we use logical connectives as field operations ($\eand$ and $\exor$
for $*$ and $+$ respectively) in $\mathbb{F}_2$ and add $\enot$ and
$\eor$ as trivial but convenient extensions. The correctness of this
operation is characterized as follows.
\begin{lemma}
  \label{lemma-solves}
  %For all $\stores$ and $\be$ with $\vars(\be) \subseteq \dom(\stores)$,
  $(\solve{\stores}{\be}{\cid}) = \{ \store \in \stores \ \mid\ \lcod{\store,\be}{\cid} = 1 \}$.
\end{lemma}

>>>>

Letting $\stores$ denote sets of memories, in Figure \ref{fig-solve}
we define the algorithm $\solve{\stores}{\be}{\cid}$ which filters a
given $\stores$ to obtain the subset whose elements satisfy $\be$. In
this Figure and elsewhere we use logical connectives as field
operations ($\eand$ and $\exor$ for $*$ and $+$ respectively) in
$\mathbb{F}_2$ and add $\enot$ and $\eor$ as trivial but convenient
extensions. The correctness of this operation is characterized as
follows.
\begin{lemma}
  \label{lemma-solves}
  %For all $\stores$ and $\be$ with $\vars(\be) \subseteq \dom(\stores)$,
  $(\solve{\stores}{\be}{\cid}) = \{ \store \in \stores \ \mid\ \lcod{\store,\be}{\cid} = 1 \}$.
\end{lemma}
